\documentclass[margin,line,11pt,letterpaper]{res}

    \usepackage[colorlinks=false]{hyperref}
    \hypersetup{
        colorlinks=false,
        linkcolor=blue,
        filecolor=magenta,      
        urlcolor=cyan,
    }

    % Side section header styling
    \let\oldsection\section
    \renewcommand{\section}[1]{\vspace{-2mm}\oldsection{\small\sc {#1}}}
    
\begin{document}
\newsectionwidth{1in}

\name{\makebox[\resumewidth]{{\LARGE Gabriel Britain} \hfill}}

\address{}

\begin{resume}
    \vspace{-7mm}
    \section{Contact Information}
    Mail: \href{mailto:quontas@gmail.com}{quontas@gmail.com}\\
    Website: \url{https://gabrielbrita.in}\\
    GitHub: \url{https://github.com/SaltyQuetzals}

    \section{Education}

    \begin{format}
        \employer{l}\location{r}\\
        \title{l}\dates{r}\\
        \body\\
    \end{format}

    \employer{\textbf{Texas A\&M University}}
    \title{\textit{BS in Computer Science, 3.72/4.0 GPA}}
    \dates{\textit{August 2016 - Expected May 2020}}
    \location{College Station, TX}
    \begin{position}
        \vspace{-3mm}\\
        Coursework: Human-Computer Interaction, NLP, Analysis of Algorithms, Data Structures
    \end{position}

    \section{Work Experience}

    \employer{\textbf{Google}}
    \title{\textit{Software Engineer Intern}}
    \dates{\textit{May 2019 - August 2019}}
    \location{Sunnyvale, CA}
    \begin{position}
        \vspace{-3mm}
        \begin{list2}
            \item Created customer-facing, real-time notification system for Google Voice enterprise customers.
            \item Integrated system into multiple teams' codebases to provide instantaneous data consistency.
        \end{list2}
    \end{position}

    \employer{\textbf{Interface Ecology Lab}}
    \title{\textit{Undergraduate Researcher}}
    \dates{\textit{February 2019 - Present}}
    \location{College Station, TX}
    \begin{position}
        \vspace{-3mm}
        \begin{list2}
            \item{Developing real-time collaborative web app that implements writing, sketching, chat, and live streaming video.}
            \item{Built developer-friendly clusters for running multi-container architecture locally, simplifying development process.}
        \end{list2}
    \end{position}

    \employer{\textbf{Google}}
    \title{\textit{Site Reliability Engineer Intern}}
    \dates{\textit{May 2018 - August 2018}}
    \location{Sunnyvale, CA}
    \begin{position}
        \vspace{-3mm}
        \begin{list2}
            \item Created automated document classification pipeline, speeding up document reviewal process by 50\%.
            \item Integrated new pipeline into application designed to manage company-wide resilience tests.
            \item Overhauled existing interface based on stakeholder feedback and included new pipeline output.
        \end{list2}
    \end{position}

    \employer{\textbf{State Farm Insurance}}
    \title{\textit{Software Engineer Intern}}
    \dates{\textit{May 2017 - August 2017}}
    \location{Richardson, TX}
    \begin{position}
        \vspace{-3mm}
        \begin{list2}
            \item Created full-stack web application to index automated test suite for engineers to search through.
            \item Application performed cosine similarity queries on user queries to provide ranked results.
            \item Released completed application to 100+ developers and improved test creation time by 40\%.
        \end{list2}
    \end{position}


    \section{Projects}

    \begin{format}
        \title{l}\dates{r}\\
        \body\\
    \end{format}

    \title{\href{https://github.com/tamuhack-org}{\textbf{TAMUhack Software Suite}}}
    \dates{\textit{January 2019 - Present}}
    \begin{position}
        \vspace{-3mm}
        \begin{list2}
            \item Created full-stack registration system in Django with 800+ users.
            \item Constructed GitOps CI/CD pipeline, reducing deployment time by over 90\%.
            \item Deployed Kubernetes cluster to Google Cloud Platform for high resiliency and uptime.
        \end{list2}
    \end{position}

    \title{\href{https://github.com/good-bull-schedules/Good-Bull-Schedules}{\textbf{Good Bull Schedules}}}
    \dates{\textit{January 2017 - May 2018}}
    \begin{position}
        \vspace{-3mm}
        \begin{list2}
            \item Created first public, open-data API for processing Texas A\&M course data.
            \item Designed responsive scheduling application for students to plan their upcoming schedule.
            \item Implemented a constraint satisfaction solver to generate optimal schedules for students.
        \end{list2}
    \end{position}

    \section{Activities}

    \begin{format}
        \title{l}\dates{r}\\
        \body
    \end{format}

    \title{\textbf{TAMUhack Tech Organizer}}\dates{\textit{January 2019 - Present}}
    \begin{position}\vspace{-7mm}\end{position}
    \title{\textbf{Aggie Coding Club Vice President}}\dates{\textit{January 2018 - Present}}
    \begin{position}\vspace{-7mm}\end{position}

    \section{Awards}

    \begin{format}
        \title{l}\dates{r}\\
        \body
    \end{format}

    \title{\textbf{National Hispanic Recognition Program Scholar}}
    \dates{\textit{May 2015}}
    \begin{position}
        \vspace{-0.001mm}
        \begin{list2}
            \item Received award presented to the top 5,000 Hispanic students out of 250,000 who take the PSAT for outstanding academic achievements.
        \end{list2}
    \end{position}

    \section{Skills}
    \renewcommand{\linespread}{5}
    \textbf{Languages}:
    Python, TypeScript/JavaScript, HTML/CSS, Java, C++, Rust, Go, C\\
    \textbf{Tools}:
    Git, Linux, BASH, WebSockets, Node.js, Docker, Kubernetes, Protobuffers, TravisCI
\end{resume}
\end{document}
